---
title: "Alcohol vs Seat choice"
author: "kimberly Lemus Munoz"
date: "summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

Based on the boxplot the back rows consumes more alcohol than both the front and the middle rows.


## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```
The mean for the back rows is three times as high as the middle rows and nearly five times as high as the front rows.


## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
 Since the p value from one way anova was such a small number we are going to follow up with a tukeyhsd.

```{r}
plot(TukeyHSD(model1))
```

Since the confidence intervals of the front-back and the middle-back are below zero that shows they are significantly different.





## Conclusions
The back rows consumed more alcohol than the middle and the front rows. This is evident by the mean of the back rows being significantly larger than that of the middle and front rows.


