---
title: "Alcohol vs Seat choice"
author: "kimberly Lemus Munoz"
date: "summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```


The people in the back seat have a higher consumption of alcohol compared to the people in the middle and the front seat. The median for the people in the back is higher than the top 75 % of teh front seat and the middle seat people.

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```
The mean for the people in the back has about three times as many of the people in the middle seats and even more than the people in the front as well.



## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
 

```{r}
plot(TukeyHSD(model1))
```



The line represents a 95 confidence interval about where the difference and it doesn’t have zero it. When we compare the middle and the back row it grows bigger than the middle row so when going to subtract the got to get the confidence interval is full of negative numbers, but finally we compare the middle in the front row and zero is in that confidence interval. They live above the zero is gone away. Since no line is cut there is a difference.


## Conclusions
I have concluded that most people in the back had the most drink they were the highest in the mean as mean in the alcohol they consumed. The middle row had the most people in it about double with the front and the people in the back seat.


